### 2016-02-08 paper.tex
Modified Section 1 and Section 3. New algorithm for PUF

We propose to construct PUFs using mixed-signal components such as {\em analog to
digital converters} (ADCs) and {\em digital to analog converters} (DACs).
As their names suggest, ADCs convert analog voltage signals 
to equivalent digital data, while DACs convert digital data into the corresponding
analog voltage. These devices are omnipresent in embedded 
systems such as mobile phones, wireless sensor nodes, smart tablets, etc.
and are often integrated into micro-controllers~\cite{xxx}. 
In mobile phones for instance, DACs are used to sample audio signals and convert
them into the digital domain, while ADCs to drive the phone's speaker.

@@

\begin{figure}[!b]
\centering
\caption{Mixed-Signal PUF in a Micro-controller with built-in ADC and DAC. }
\includegraphics[width=6cm]{figs/mspuf}
\end{figure}

The scheme for the MS-PUF is shown in Figure~\ref{fig:mspuf}. An output of a DAC channel
is connected to the input of the ADC. A {\em challenge} in the form of a
digital time-series pattern is transferred to the DAC from the processor. This signal is
converted to analog at the DAC's output. The ADC quantifies and reconverts the signal 
into a time-series digital pattern. This ADC output is the {\em response} to the challenge.
Since the ADC and DAC are accessible from the processor, a software program can create 
create a challenge and read the corresponding response. 
The response is affected by many factors including the quantification and environmental
noise, and inherient variations due to the fabrication variations of the ADC and the 
DAC. The latter aspect is the focus for constructing the PUF.

@@

{\flushleft \em Construction of the MS-PUF. }
The MS-PUF is created by connecting an output of a DAC to an
input channel of an ADC. This creates a loop between the processor
core, the DAC, and the ADC as shown in Figure~\ref{fig:ms-puf}.
The sofware running on the processor core 
generates a challenge in the form of a time-series pattern
comprising of $n$-bit digital values, which are transferred one at a time
to the DAC. Each digital value is converted to an analog voltage (or
current) and reconverted to a representative $m$-bit digital value by the ADC.
The software program reads the
ADC output and forms the response to the challenge using a function $g$.
Algorithm~\ref{algo:puf_sw} has the details.

\begin{algorithm}[!ht] \label{algo:puf_sw}
\begin{scriptsize}
	\caption{\emph{Software Program for the MS-PUF}}
	\DontPrintSemicolon
	\KwIn{$\mathbf C$ : an array representing the challenge}
	\KwOut{$\mathbf R$ : an array representing the response}
	\Begin{
		\For{$i \in \{1, 2, \cdots len(\mathbf C)\}$}{
			Output\_to\_DAC($\mathbf C_i$); \\
			/* Wait for ADC to finish conversion */ \;
			$r$ = Input\_from\_ADC(); \;	
			$\mathbf R_i = g(C_i, r)$ \;
		}
		\Return ${\mathbf R}$
	}
\end{scriptsize}
\end{algorithm}

In every iteration in Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit reply from 
the ADC is the result of the $n$-bit DAC input $\mathbf C_i$
undergoing a conversion to analog followed by a reconversion to digital.
Typically $m$ and $n$ are $8$, $12$, $16$, or $24$ bits. 
Due to reasons such as quatification and ambient noise, the reply
$r$ would be different from $\mathbf C_i$. Further, due to nano-scale
variations between devices, $r$ would vary from one device
to another.  There are several potential reasons for variations 
between devices.
A DAC output for instance, is influenced by several nano-scale features such 
as voltage references, resistor tolerances, 
capacitive effects, and amplifier differences. This could result 
in two DACs having different responses to the same input. 
Successive approximation ADCs have built in DACs, therefore
would be affected by the same variations as the DAC. Additionally,
other components in the ADC such as sample and hold circuits and
comparators could lead to differences in the reply.

 could cause two DACs to have different responses

 such as the tolerance

Nano scale variations in DACs and ADCs.

>>>>

We propose to construct PUFs using mixed-signal components such as {\em analog to
digital converters} (ADCs) and {\em digital to analog converters} (DACs).
As their names suggest, ADCs convert analog voltage signals 
to equivalent digital data, while DACs convert digital data into the corresponding
analog voltage. These devices are omnipresent in embedded 
systems such as mobile phones, wireless sensor nodes, smart tablets, etc.
and are often integrated into micro-controllers~\cite{xxx}. Several 
micro-controller vendors have multiple DACs and ADCs built into a
single device.

@@

\begin{figure}[!b]
\centering
\caption{Mixed-Signal PUF in a Micro-controller with built-in ADC and DAC.\label{fig:mspuf} }
\includegraphics[width=6cm]{figs/mspuf}
\end{figure}

The scheme for the MS-PUF is shown in Figure~\ref{fig:mspuf}. Outputs of DACs in the device
are fedback to the inputs of ADCs to form feedback channels. 
The DAC in each channel would receive digital data from the processor and convert it
to an equivalent analog value. The ADC at the other end of the channel would reconvert
the analog value to a corresponding digital data. The reconverted digital data would 
be affected by several factors including quantification and environmental noise,
and inherient variations due to the fabirication of the ADCs and DACs. The latter
aspect is useful for constructing PUFs.

The PUF {\em challenge} is a 
digital time-series pattern and a random sequence of feedback channel identifiers. 
The time-series pattern is transferred to the first channel in the sequence and the 
and the result read from the corresponding ADC. This result is a time-series 
digital pattern and is sent to the next channel in the sequence. This `looping' of the
pattern continues for every channel in the sequence. The result after the final loop
is taken as the PUFs {\em response}.

@@

{\flushleft \em Constructing the MS-PUF. }
The MS-PUF is created by connecting outputs of DAC to an
input channel of an ADC. This creates loops between the processors
cores, DACs, and ADCs as shown in Figure~\ref{fig:ms-puf}.
If there are $n$ DACs and $m$ ADCs in the device
(and $n \le m$), then $n$ such loops are made resulting in $n$ feedback channels.
The PUFs challenge is a time-series pattern comprising of
$\alpha$-bit digital values and a sequence of random channel identifiers.
The response is a time-series pattern comprising of $\beta$-bit digital 
values obtained from the ADC. The values for $\alpha$ and $\beta$ are
respectively dependent on the DAC and ADC resolutions. Typically, $\alpha = \beta$
for a device and have values 8, 12, 16, or 24.

Algorithm~\ref{algo:puf_sw} depicts the MS-PUF. 
The sofware running in the processor core 
selects the first channel from the sequence ($\mathbf L$) and 
transfers the time-series digital pattern to the corresponding
DAC one value at a time ({\em line~5}). Each digital value is converted to an analog voltage (or
current) and reconverted to a representative digital value by the ADC.
The software program reads these values from the ADC to form a new digital time-series 
pattern ({\em line~7}). This pattern forms the input to the next channel in the sequence. The process
is repeated for the entire sequence. A function $g$ processes the initial pattern ($\mathbf C$) and 
the final pattern formed (corresponding to $\mathbf L_{len(L)}$) to form the PUFs response.

\begin{algorithm}[!ht] \label{algo:puf_sw}
\begin{scriptsize}
	\caption{\emph{MS-PUF : Obtaining the Response to a Challenge}}
	\DontPrintSemicolon
 	\LinesNumbered
	\KwIn{$(\mathbf C,\mathbf L)$ : (an array representing digital time-series pattern, 
                                         a random sequence of channel identifiers)}
	\KwOut{$\mathbf R$ : an array representing the response}
	\Begin{
		$\mathbf T \leftarrow \mathbf C$ \;
		\For{$i \in \{1, 2, \cdots, len(\mathbf L)\}$}{
			\For{$j \in \{1, 2, \cdots, len(\mathbf T)\}$}{
				Output\_to\_DAC($\mathbf T_j$, $\mathbf L_i$); \\
				/* Wait for ADC to finish conversion */ \;
				$r$ = Input\_from\_ADC($\mathbf L_i$); \;	
				$\mathbf T_j \leftarrow r$ \;
			}
		}
		$\mathbf R \leftarrow g(\mathbf C, \mathbf T)$ \;
		\Return ${\mathbf R}$
	}
\end{scriptsize}
\end{algorithm}

In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $\beta$-bit 
reply from the ADC is the result of $\alpha$-bit DAC input $\mathbf T_j$ 
undergoing a conversion to analog followed by a reconversion to digital. 
Due to reasons such as quatification and ambient noise, the result ($r$)
would be different from $\mathbf T_j$ even if $\alpha = \beta$.

Due to nano-scale variations, devices would inject certain randomness into
$r$ that would depend on the channel used and would vary from one device to another.

There are several potential reasons for variations 
between devices.
A DAC output for instance, is influenced by several nano-scale features such 
as voltage references, resistor tolerances, 
capacitive effects, and amplifier differences. This could result 
in two DACs having different responses to the same input. 
Successive approximation ADCs have built in DACs, therefore
would be affected by the same variations as the DAC. Additionally,
other components in the ADC such as sample and hold circuits and
comparators could lead to differences in the reply.
